Multisensor Architecture for an Intersection Management System

### 2015-04-07 ch2-mdf_ims.tex
Added fourth IMS component paragraph, Communication

>>>>

One of the keypoints of ITS is how information technologies and communication advances are included in transportation. The main goal of this is to allow that information to be shared between vehicles and infrastructure entities. For this reason, 3 communication approaches appear: Vehicle-to-vehicle or Inter-vehicle communication (V2V), vehicle-to-infrastructure communication (V2I) and vehicle to both vehicle and infrastructure (V2X). Several protocols and standars have been proposed for these communication approaches, for example DSRC, WAVE and IEEE 802.11p, but research and development on this component is still active.
